Differentially Private Bayesian Inference

### 2018-06-18 main.tex
update notes

	Every candidate will occupy a portion of 1 as their output probability. Suppose candidates within three steps from the correct answer are good answers, the portion occupied by the good answer are decreasing when the size of candidate set increasing. That's to say, the probability of outputting good answer are decreasing when the data size and dimension of prior distribution are increasing. More specifically, the candidate set size is $\sim n^{m-1}$, which means the probability of outputting good answers are decreasing with speed $\sim n^{m-1}$.

@@

	From analysis above, we can see the probability of output the good answer will not changed a lot as the size of the candidate set increasing. Specifically, we can easily have the two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$. As a results, the probability of outputting good answers are decreasing with speed upper bounded by $(m-1)! \times 2^{m-1}$, which is much more smaller than in exponential mechanism. Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.

>>>>

	Each candidate will occupy a portion of ``$1$'' as their outputting probability. Suppose candidates within three steps from the correct answer are good answers, the portion occupied by the good answer are decreasing when the size of candidate set increasing. That's to say, the probabilities of outputting good answers are decreasing when the data size and dimension of prior distribution increasing. More specifically, the candidate set size is $\sim n^{m-1}$, which means the probability of outputting good answers are decreasing with speed $\sim n^{m-1}$.

@@

	From analysis above, we can see the probability of output the good answer will not changed a lot as the size of the candidate set increasing. Specifically, we can easily have the two upper bounds: $|S_{noise}| \leq (m-1)$ and $|L_{noise/0}| \leq (m-1)$. As a result, the probabilities of outputting good answers are decreasing with speed upper bounded by $(m-1)! \times 2^{m-1}$. Since $n \gg 2$ and $m$ is usually smaller than $10$, it is easy to see that the decay speed $(m-1)! \times 2^{m-1}$ in Laplace mechanism is much more smaller than $n^{m-1}$ in our exponential mechanism. Moreover, when the steps are small, $0$ for example, $|S_{noise}| = |L_{noise/0}|  = 0$, which means the probability of correct answer will decrease very little no matter how large the candidate set is.
